%%
%% This is file `squelette-rr.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% RR.dtx  (with options: `sample')
%% ********************************************************************
%% Copyright (C) 1997-1999 2004 2006-2011 INRIA/APICS/MARELLE by Jose' Grimm
%% This file may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%% An archive of the software can be found at
%%    ftp://ftp-sop.inria.fr/marelle/RR-INRIA

\documentclass[twoside]{article}
\usepackage[a4paper]{geometry}
\usepackage[latin1]{inputenc} % ou \usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} % ou \usepackage[OT1]{fontenc}
\usepackage{lmodern}
\usepackage{RR-LIMOS}
\usepackage{hyperref}
%%\usepackage[frenchb]{babel} % optionnel
\RRNo{00042}
%%
%% date de publication du rapport
\RRdate{September 2012}
%%
%% Cas d'une version deux
%% \RRversion{2}
%% date de publication de la version 2
%% \RRdater{November 2008}
%%
\RRauthor{% les auteurs
 % Premier auteur, avec une note
Jos\'e Grimm\thanks{Footnote for first author}%
  % note partag\'ee (optionnelle)
  \thanks[sfn]{Shared foot note}%
 % \and entre chaque auteur s'il y en a plusieurs
  \and
Philippe Louarn\thanks{Footnote for second author}%
 % r\'ef\'erence \`a la note partag\'ee
\thanksref{sfn}
 % liste longue pour tests de mise en page
\and Nicolas Bourbaki\thanks{etc} \and Andr\'e Lichnerowicz
\and Marcel-Paul Sch\"utzenberger \and Jacques-Louis Lions}
%% Ceci apparait sur chaque page paire.
\authorhead{Grimm \& Louarn \& others}
%% titre francais long
\RRtitle{Exemple de document\\
 utilisant le style\\rapport de recherche\\Inria}
%% English title
\RRetitle{Very Long Title for Checking Whether it Fits on the Cover
  Page of Inria's Research Report Document Type (Extended Version)}
%%
\titlehead{Example of RR.sty}
%%
\RRnote{This is a note}
\RRnote{This is a second note}
%%
\RRresume{Ce document montre comment utiliser le style RR.sty.
Pour en savoir plus, consulter le fichier RR.dvi ou RR.pdf.
D\'efinissez toujours les commandes avant utilisation.
}
\RRabstract{
Our society relies increasingly on digital technologies to communicate,
seek medical information, travel, or have fun. These often-invisible
technologies simplify our tasks and enrich our daily lives, while also
developing the economy. At the interface of computer science and
mathematics, from pure research to technological development and to
industrial transfer, researchers at Inria, a public research institute,
are inventing tomorrow's digital technologies. Inria's research is
collaborative, which is evidenced by the diversity of the talent
comprising its research teams, as well as in the many joint projects
conducted with public and private research entities in France and
abroad. While competing with the leading international specialists in
their field, Inria researchers and staff are also committed to sharing
their knowledge with the widest possible audience.

Computational technologies are currently used to increase the
efficiency and safety of our transport services, introduce smart
applications into homes, and develop agricultural practices that are
better for the environment... They are also behind a range of new
services, and are bringing about fundamental changes in the ways we
live our lives, improving them on a day-to-day basis. }
%%
\RRmotcle{calcul formel, base de formules,  %mots-cl\'es sans rapport
protocole, diff\'erentiation automatique, % les uns avec les autres
g\'en\'eration de code,  mod\'elisation, lien symbolique/num\'erique,
matrice structur\'ee, r\'esolution de syst\`emes polynomiaux}
\RRkeyword{task placement, environment, % keywords (taken from some
 message passing,  network management,   % random research report)
 performances}
%%
%% \RRprojet{Apics}  % cas d'un seul projet
\RRprojets{HPC Benny}
%%
%% \URLorraine % pour ceux qui sont \`a l'est
%% \URRennes  % pour ceux qui sont \`a l'ouest
%% \URRhoneAlpes % pour ceux qui sont dans les montagnes
%% \URRocq % pour ceux qui sont au centre de la France
%% \URFuturs % pour ceux qui sont dans le virtuel
%% \URSophia % pour ceux qui sont au Sud.
%%
%% \RCBordeaux % centre de recherche Bordeaux - Sud Ouest
%% \RCLille % centre de recherche Lille Nord Europe
%% \RCParis % Paris Rocquencourt
%% \RCSaclay % Saclay \^Ile de France
%% \RCGrenoble % Grenoble - Rh\^one-Alpes
%% \RCNancy % Nancy - Grand Est
%% \RCRennes % Rennes - Bretagne Atlantique
\RCLimos % Sophia Antipolis M\'editerran\'ee

%%
\begin{document}
%%
\makeRR   % cas d'un rapport de recherche
%% \makeRT % cas d'un rapport technique.
%% a partir d'ici, chacun fait comme il le souhaite
\section{First section}
Here is some text for the first section, and a label\label{sec1}.
Uses version \RRfileversion\ of the package.\newpage
\section{Second section}
Text for the second section. This is closely related to the text in
section \ref{sec1} on page \pageref{sec1}. \newpage
\tableofcontents

\end{document}
\endinput
%%
%% End of file `squelette-rr.tex'.
